{\bf Stateless Model Checking \\ with Data-Race Preemption Points}

### 2016-03-01 oopsla/calcm.tex
Finish 1st draft of calcm slides

\begin{frame}{1. Finding more bugs with data-race PPs}
\end{frame}

\begin{frame}{2. Finding the same bugs... slower}
\end{frame}

\begin{frame}{3. Nondeterministic data-race candidates}
\end{frame}

\begin{frame}{4. Total verification}
\end{frame}

>>>>

\begin{frame}{1. Finding more bugs with data-race PPs}
	\begin{center}
		\includegraphics[width=0.6\textwidth]{eval1.pdf}
	\end{center}
	\begin{itemize}
		\item 17-118 seconds: Quicksand loses on parallelization/startup overhead
			%\begin{itemize}
			%	\item (remember: Quicksand on 10 CPUs, control on 1)
			%\end{itemize}
		\item Ultimately, 180\% as many bugs in total!
	\end{itemize}
\end{frame}

\begin{frame}{2. Finding the same bugs... slower}
	\begin{center}
		\includegraphics[width=0.6\textwidth]{eval2.pdf}
	\end{center}
	\begin{itemize}
		\item ICB outperforms Iterative Deepening when using the same PPs
		\item Suggests Quicksand could incorporate ICB in its scheduling strategy
	\end{itemize}
\end{frame}

\begin{frame}{3. Nondeterministic data-race candidates}
	Some data races come from code that executes only nondeterministically.
	\begin{itemize}
		\item In a single-execution data race analysis, these accesses won't be seen.
		\item MC can uncover the racy logic, identify a new PP, and find more bugs.
	\end{itemize}

	\begin{center}
		\includegraphics[width=0.7\textwidth]{eval3.pdf}
	\end{center}
\end{frame}

\begin{frame}{4. Total verification}
	\begin{center}
		\includegraphics[width=0.6\textwidth]{eval4.pdf}
	\end{center}
	\begin{itemize}
		\item If no data-race candidates, can verify with sync API PPs alone.
		\item Data-race PPs allow total verification of 425\% as many tests!
		\item ICB slower to verify than single-pass DPOR due to repeated work.
	\end{itemize}
\end{frame}
